### 2012-04-11 docs/analysis/analysis.tex
point to AmrPostprocessing

\section{The {\tt data\_processing} Routines}
\label{sec:analysis}

The {\tt fParallel/data\_processing/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

The routine {\tt fspeciesmass2d.f90} in {\tt
  data\_processing/tutorial} serves as a well-commented example of how
to work with \maestro\ plotfile data.  This routine simply computes
the total mass of a particular species on the entire domain for a 2-d
dataset.  It is written to understand a multilevel (AMR) dataset, and
only considers the finest-available data at any physical location in
the computational domain.

@@

As a concrete example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt fParallel/data\_processing/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/MAESTRO/fParallel/data_processing/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

>>>>

\section{The {\tt AmrPostprocessing} Routines}
\label{sec:analysis}

The {\tt AmrPostprocessing/F\_Src/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

The routine {\tt fspeciesmass2d.f90} in {\tt
  F\_src/tutorial} serves as a well-commented example of how
to work with \maestro\ plotfile data.  This routine simply computes
the total mass of a particular species on the entire domain for a 2-d
dataset.  It is written to understand a multilevel (AMR) dataset, and
only considers the finest-available data at any physical location in
the computational domain.

@@

As a concrete example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt AmrPostprocessing/F\_Src/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/AmrPostprocessing/F_Src/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}
